\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-14 submission/manuscript.Rmd
update

<!-- stakes and Post-truth era -->
For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations  indistinguishable from reality. These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022]. Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020]. This challenge is  thus central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack  thereof) between authentic and simulated objects will play a critical role.

<!-- Ambiguous stimuli and irrelevance of objective features -->
While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain  key details and an overall appearance of reality), it is fair to assume that these technical limitations will become  negligible in the near future. In fact, in the field of face perception and recognition, recent research found images of  artificially-generated faces to be perceived as more real than real faces [@nightingale2022; @tucciarelli2020; @moshel2022]. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective  characteristics (for instance, facial features in the perception of real relative to fake faces; [@holmes2016; @moshel2022]), how can we make judgments regarding their nature?

@@

<!-- Attractiveness -->
Images of faces, one of the most common artificial intelligence (AI) targets, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF). Talk about possible links between attractiveness and simulation monitoring

>>>>

<!-- stakes and Post-truth era -->
For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations indistinguishable from reality. These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022]. Such advancements not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020]. This challenge is thus central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack  thereof) between authentic and simulated objects will play a critical role.

<!-- Ambiguous stimuli and irrelevance of objective features -->
While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details and an overall appearance of reality; cf "the uncanny valley effect"; [@mcdonnell2010face]), it is fair to assume that these technical limitations will become  negligible in the near future. In fact, in the field of face perception and recognition, recent research found images of  artificially-generated faces to be perceived as more real than real faces [@nightingale2022; @tucciarelli2020; @moshel2022]. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective  characteristics (for instance, facial features in the perception of real relative to fake faces; [@holmes2016; @moshel2022]), how can we make judgments regarding their nature?

@@

<!-- Attractiveness -->
Images of faces, one of the most common artificial intelligence (AI) targets, integrate components of emotional reaction, salience, self-relevance via attractiveness (REF). Talk about possible links between attractiveness and simulation monitoring
